---
title: "Experiment 2a: Analysis of Root Questions, NoContext"
author: "mcmoyer"
date: "March 30, 2021"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(tidyverse)
theme_set(theme_bw())

this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")

cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
```

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d = read.csv("../data/normed_nocontext_root.csv")

d$ModalPresent = as.factor(d$ModalPresent)
d$Wh = as.factor(d $Wh)
d$paraphrase = as.factor(d$paraphrase)
```

```{r, include=FALSE, warning=FALSE, echo=FALSE}
d.ms.ma = d %>%
  filter(paraphrase %in% c("a","every")) %>%
  # hand-code paraphrase so mean-centering is more interpretatble 
  # (otherwise, "every" will be 1 and "a" will be 0 by default)
  mutate(paraphrase.dc = recode(paraphrase, "a" = 1, "every" = 0) ) %>%
  # mean-center
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))


```

# Is rating modulared by Paraphrase, Wh and ModalPresent?

- only 2-way: Wh and Modal Present, and Wh and Paraphrase
- No paraphrase and ModalPresent
- Bias for MS,but ModalPresent actually decreases the difference between MS and MA (Modal Questions overall higher than NoModal)


```{r}
# m.ms.ma.full = lmer(normed_rating ~ cParaphrase*Wh*cModalPresent + (1+cParaphrase+Wh+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma.full, "model-msma-full.rds")

m.ms.ma.full <- readRDS("model-msma-full.rds")
summary(m.ms.ma.full)
```


# Wh-word sub-models

## What
```{r}
d_what = d.ms.ma %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.what = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_what) 
summary(m.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# summary(m.what.simple)
```

## How
```{r}
d_how = d.ms.ma %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.how = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_how) 
summary(m.how)

# m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
# summary(m.how.simple)
```

## Where
```{r where model}
d_where = d.ms.ma %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.where = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where) 
summary(m.where)

m.where.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where)
summary(m.where.simple)
```

## WHY
```{r why model}
d_why = d.ms.ma %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.why = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
summary(m.why)

m.why.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why)
summary(m.why.simple)
```

## Who
```{r who model}
d_who = d.ms.ma %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.who = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id), data=d_who) 
summary(m.who)

m.who.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id), data=d_who)
summary(m.who.simple)
```

## When
```{r when model}
# have to use less random effects structure
d_when = d.ms.ma %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.when = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase|tgrep_id), data=d_when) 
summary(m.when)

# simple effects
m.when.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|tgrep_id), data=d_when)
summary(m.when.simple)
```
# Is there an overall bias for MA? Does paraphrase predict the rating?
- No: going from MS to MA decreases the ratings, meaning that there is an MS b
```{r}
# m.ms.ma = lmer(normed_rating ~ cParaphrase + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma, "model-msma.rds")

m.ms.ma <- readRDS("model-msma.rds")
summary(m.ms.ma)
```

# Are MS ratings modulated by linguistic form factors?
- yes, by the presence of a modal, which increases ratings
- one 2-way interaction wtih where vs when
```{r}
d.ms = d %>% 
  filter(paraphrase=="a") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

# m.ms = lmer(normed_rating ~ cModalPresent*Wh + (1+Wh+cModalPresent|workerid) + (1|tgrep_id), data=d.ms)
# saveRDS(m.ms, "model-ms.rds")

m.ms <- readRDS("model-ms.rds")
summary(m.ms)

```


# Are MA ratings modulated by linguistic form factors?
- signficant three-way interactions
- modals increase MA ratings too
- 
```{r}
d.ma = d %>% 
  filter(paraphrase=="every") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

# m.ma = lmer(normed_rating ~ cModalPresent*Wh + (1+Wh+cModalPresent|workerid) + (1|tgrep_id), data=d.ma)
# saveRDS(m.ma, "model-ma.rds")

m.ma <- readRDS("model-ma.rds")
summary(m.ma)
```


# Other Models

```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# Set the reference levels
contrasts(d$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

contrasts(d$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))
centered = cbind(d,myCenter(d["ModalPresent"]))
```

# Full Model with all paraphrases

- Significant three-way interactions with Task for 'the' compared to 'every'
- Significant two-way for 'a' versus 'every' 
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# m.full = lmer(normed_rating ~ cModalPresent*Wh*paraphrase + (1+paraphrase+Wh+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=centered,REML=FALSE)
# saveRDS(m.full, "model-nocontext-root-full.rds")

nocontext_model <- readRDS("model-nocontext-root-full.rds")
summary(nocontext_model)
```

# Models broken up by Wh for all paraphrases

## What
- biased for 'the', and overall modal questions higher ratings
- adding a modal slightly decreases the difference between 'the' and 'every'
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# "what" model
d_what = centered %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
contrasts(d_what$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))

# m.what = lmer(normed_rating ~ cModalPresent*paraphrase + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# saveRDS(m.what, "model-nocontext-root-what.rds")

m.what <- readRDS("model-nocontext-root-what.rds")
summary(m.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what) 
# summary(m.what.simple)
```

## How
- modal questions increase the difference between 'every' and 'a', and decrease the difference between 'every' and 'the'
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# "how" model
d_how = centered %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  droplevels()
contrasts(d_how$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))

# m.how = lmer(normed_rating ~ cModalPresent*paraphrase + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_how)
# saveRDS(m.how, "model-nocontext-root-how.rds")

m.how <- readRDS("model-nocontext-root-how.rds")
summary(m.how)

# m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
# summary(m.how.simple)
```

## Where
- no effect of modal at all (marginal 2-way interaction)
- ratings increase significantly from 'every' to 'the' and 'every' to 'a'
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# "where" model
d_where = d %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  droplevels()
contrasts(d_where$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))

# m.where = lmer(normed_rating ~ cModalPresent*paraphrase + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_where)
# saveRDS(m.where, "model-nocontext-root-where.rds")

m.where <- readRDS("model-nocontext-root-where.rds")
summary(m.where)

# m.where.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_where) 
# summary(m.where.simple)
```

## Why
- no effect of modal at all
- ratings increase significantly from 'every' to 'the' and 'every' to 'a'
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
d_why = d %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  droplevels()
contrasts(d_why$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))

# m.why = lmer(normed_rating ~ cModalPresent*paraphrase + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_why)
# saveRDS(m.why, "model-nocontext-root-why.rds")

m.why <- readRDS("model-nocontext-root-why.rds")
summary(m.why)

# m.why.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_why) 
# summary(m.why.simple)
```

## Who
- 2-way interaction: modal increases ratings from 'every' to 'a'
- ratings increase from 'every' to 'the' but no interaction
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
d_who = d %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  droplevels()
contrasts(d_who$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))

# m.who = lmer(normed_rating ~ cModalPresent*paraphrase + (1+paraphrase|workerid) + (1+paraphrase|tgrep_id), data=d_who)
# saveRDS(m.who, "model-nocontext-root-who.rds")

m.who <- readRDS("model-nocontext-root-who.rds")
summary(m.who)

# m.who.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|workerid) + (1+paraphrase|tgrep_id), data=d_who) 
# summary(m.who.simple)
```

## When
- 'a' ratings increased compared to 'every'
- 2-way interaction: 'the' ratings already increased compared to 'every', but not as much for modal questions
```{r, eval=FALSE, warning=FALSE, echo=FALSE}
# have to use less random effects structure
d_when = d %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  droplevels()
contrasts(d_when$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))

# m.when = lmer(normed_rating ~ cModalPresent*paraphrase + (1+paraphrase|tgrep_id), data=d_when)
# saveRDS(m.when, "model-nocontext-root-when.rds")

m.when <- readRDS("model-nocontext-root-when.rds")
summary(m.when)

# simple effects
# m.when.simple = lmer(rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_when) 
# summarynormed_rating
```
