---
title: 'Experiment 1a: Analysis of Root Questions, Context'
author: "mcmoyer"
date: "September 20, 2021"
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
theme_set(theme_bw())

this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")

# set the color palette for color-blind
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999")

# Read the data in
d = read.csv("../data/normed.csv")
```


```{r, include=FALSE, warning=FALSE, echo=FALSE}
d$ModalPresent = as.factor(d$ModalPresent)
d$Wh = as.factor(d$Wh)
d$paraphrase = as.factor(d$paraphrase)
contrasts(d$paraphrase)
#       every the
# a         0   0
# every     1   0
# the       0   1

contrasts(d$Wh)
#       what when where who why
# how      0    0     0   0   0
# what     1    0     0   0   0
# when     0    1     0   0   0
# where    0    0     1   0   0
# who      0    0     0   1   0
# why      0    0     0   0   1
```


```{r, include=FALSE, warning=FALSE, echo=FALSE}
d.ms.ma = d %>%
  filter(paraphrase %in% c("a","every")) %>%
  # hand-code paraphrase so mean-centering is more interpretatble 
  # (otherwise, "every" will be 1 and "a" will be 0 by default)
  mutate(paraphrase.dc = recode(paraphrase, "a" = 1, "every" = 0) ) %>%
  # mean-center
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(1,0,0,0,0,0),
                              "what.vs.when"=c(0,1,0,0,0,0),
                              "where.vs.when"=c(0,0,0,1,0,0),
                              "who.vs.when"=c(0,0,0,0,1,0),
                              "why.vs.when"=c(0,0,0,0,0,1))
contrasts(d.ms.ma$Wh)

#       how.vs.when what.vs.when where.vs.when who.vs.when why.vs.when
# how             1            0             0           0           0
# what            0            1             0           0           0
# when            0            0             0           0           0
# where           0            0             1           0           0
# who             0            0             0           1           0
# why             0            0             0           0           1
```

# Is rating modulared by Paraphrase, Wh and ModalPresent?
- Yes, significant three-way interactions
```{r}

# m.ms.ma.full = lmer(normed_rating ~ cParaphrase*Wh*cModalPresent + (1+cParaphrase+Wh+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma.full, "model-msma-full.rds")

m.ms.ma.full <- readRDS("model-msma-full.rds")
summary(m.ms.ma.full)
```

# Does paraphase predict rating?
- No.
```{r}
# m.ms.ma = lmer(normed_rating ~ cParaphrase + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma, "model-msma.rds")

m.ms.ma <- readRDS("model-msma.rds")
summary(m.ms.ma)
# confint(m.ms.ma)
```

# Are MS ratings modulated by linguistic form factors?
- Yes: all 2-way interactions significant
- overall 
```{r}
d.ms = d %>% 
  filter(paraphrase=="a") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ms$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

# m.ms = lmer(normed_rating ~ cModalPresent*Wh + (1+Wh+cModalPresent|workerid) + (1|tgrep_id), data=d.ms)
# saveRDS(m.ms, "model-ms.rds")

m.ms <- readRDS("model-ms.rds")
summary(m.ms)

```


# Wh-word sub-models

## What
```{r}
d_what = d.ms.ma %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.what = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_what) 
summary(m.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# summary(m.what.simple)
```

## How
```{r}
d_how = d.ms.ma %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.how = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_how) 
summary(m.how)

m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
summary(m.how.simple)
```

## Where
```{r where model}
d_where = d.ms.ma %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.where = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where) 
summary(m.where)

m.where.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where)
summary(m.where.simple)
```

## WHY
```{r why model}
d_why = d.ms.ma %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.why = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
summary(m.why)

m.why.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
summary(m.why.simple)
```

## Who
```{r who model}
d_who = d.ms.ma %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.who = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id), data=d_who) 
summary(m.who)

m.who.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|workerid) + (1+cParaphrase|tgrep_id), data=d_who) 
summary(m.who.simple)
```

## When
```{r when model}
# have to use less random effects structure
d_when = d.ms.ma %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>% 
  droplevels()

m.when = lmer(normed_rating ~ cModalPresent*cParaphrase + (1+cParaphrase|tgrep_id), data=d_when) 
summary(m.when)

# simple effects
m.when.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|tgrep_id), data=d_when) 
summary(m.when.simple)
```




# Are who-questions MA biased?

```{r}
d.ms.ma.who = d.ms.ma %>% 
  filter((Wh == "who")) %>% 
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()

m.ms.ma.who = lmer(normed_rating ~ cParaphrase + (1+cParaphrase|workerid) + (1|tgrep_id), data=d.ms.ma.who)
# saveRDS(m.ms.ma.who, "model-msmawho.rds")
# 
# m.ms.ma.who <- readRDS("model-ms.rds")
summary(m.ms.ma.who)
# confint(m.ms.ma.who)
```

# Are MA ratings modulated by linguistic form factors?
- some differences based on WH-word
```{r}
d.ma = d %>% 
  filter(paraphrase=="every") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  droplevels()
# Set the reference levels
contrasts(d.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

# m.ma = lmer(normed_rating ~ cModalPresent*Wh + (1+Wh+cModalPresent|workerid) + (1|tgrep_id), data=d.ma)
# saveRDS(m.ma, "model-ma.rds")

m.ma <- readRDS("model-ma.rds")
summary(m.ma)
```


# Other Models

```{r, eval = FALSE, echo = FALSE}
# Set the reference levels
contrasts(d$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

contrasts(d$paraphrase) = cbind("a.vs.every"=c(1,0,0),"the.vs.every"=c(0,0,1))

centered = cbind(d,myCenter(d["ModalPresent"]))
```

## full model with random slopes and intercepts
```{r full model, eval = FALSE, echo = FALSE}
# m.full = lmer(normed_rating ~ cModalPresent*Wh*paraphrase + (1+paraphrase+Wh+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=centered,REML=FALSE) 
# saveRDS(m.full, "model-context-root-full.rds")

m.full <- readRDS("model-context-root-full.rds")
summary(m.full)
```

