---
title: "Exploratory analysis of context: Regression Analysis"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(philentropy)
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
```

```{r read in all the data, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
context_root = read.csv("../../../03_experiment/data/normed.csv") 
context_root$Task <- "context"
context_root$VerbLemma <- ""
context_root = context_root[,!(names(context_root) %in% c("X"))]

context_emb = read.csv("../../../04_experiment/data/normed.csv") 
context_emb$Task <- "context"
context_emb = context_emb[,!(names(context_emb) %in% c("X"))]


nocontext_root = read.csv("../../../05_experiment/data/normed_nocontext_root.csv")
nocontext_root$VerbLemma <- ""
nocontext_root$Task <- "nocontext"
nocontext_root = nocontext_root[,!(names(nocontext_root) %in% c("X"))]

nocontext_emb = read.csv("../../../06_experiment/data/normed_nocontext_embedded.csv")
nocontext_emb$Task <- "nocontext"
nocontext_emb = nocontext_emb[,!(names(nocontext_emb) %in% c("X"))]
```

```{r join all the dfs together, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
context <- full_join(context_root,context_emb)
nocontext <- full_join(nocontext_root,nocontext_emb)
d <- full_join(context, nocontext)

# sanity check the join
nrow(context_root) + nrow(context_emb) + nrow(nocontext_root) + nrow(nocontext_emb)
nrow(d)
```


```{r}
# Make everything into a factor
d$Wh = as.factor(d$Wh)
d$workerid = as.factor(d$workerid)
d$tgrep_id = as.factor(d$tgrep_id)
d$paraphrase = as.factor(d$paraphrase)
d$ModalPresent = as.factor(d$ModalPresent)
d$Task = as.factor(d$Task)
```
# Does cTask predict rating?

```{r subset to ms/ma}
d.ms.ma = d %>%
  filter(paraphrase %in% c("a","every")) %>%
  # hand-code paraphrase so mean-centering is more interpretatble 
  # (otherwise, "every" will be 1 and "a" will be 0 by default)
  mutate(paraphrase.dc = recode(paraphrase, "a" = 1, "every" = 0) ) %>%
  mutate(cParaphrase = as.numeric(paraphrase.dc)-mean(as.numeric(paraphrase.dc))) %>%
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>%
  mutate(cTask = as.numeric(Task) - mean(as.numeric(Task))) %>%
  droplevels()
```

```{r set the reference levels for wh}
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))
```

```{r}

# m.ms.ma.full = lmer(normed_rating ~ cParaphrase*Wh*cModalPresent*cTask + (1+cParaphrase+Wh+cModalPresent|workerid) + (1+cParaphrase+cTask|tgrep_id), data=d.ms.ma)

```



# Split models up by paraphrase
## A paraphrase

```{r subset to a-paraphrase, include=FALSE, warning=FALSE, echo=FALSE}
# Subset
a_data <- d %>%
  filter(paraphrase == "a") %>%
  mutate(Task = as.factor(Task),
         cModalPresent = as.numeric(ModalPresent) - mean(as.numeric(ModalPresent)),
         cTask = as.numeric(Task) - mean(as.numeric(Task)))

# Set contrasts
# Wh Reference level = When
contrasts(a_data$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))
```

- There were no 3-way interactions, however there were significant 2-way interactions between Wh-Word and Task, and Wh-Word and Modality.
- Wh x Modality:
  - Significant positive intercept for Modality suggests that for the a-ratings for modal questions are higher than nonmodal question at the reference level
  - Significant negative intercepts for all Wh-words suggest that a-ratings decrease for all wh-questions compared to the reference level.
  - However, compared to the reference level when-questions, a-ratings are decreased even with Modal questions
- Wh-Word and Task:
  - there is no significant main effect of Task as a predictor of a-ratings, but 
  - For all Wh-Words except
```{r a-para model}
# m.a = lmer(normed_rating ~ cModalPresent*Wh*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id), data=a_data,REML=FALSE)
# saveRDS(m.a, "../models/model-contexts-a.rds")

a.model <- readRDS("../models/model-contexts-a.rds")
summary(a.model)
```

## Every paraphrase

```{r subset to every-paraphrase, include=FALSE, warning=FALSE, echo=FALSE}
# Subset
every_data <- d %>%
  filter(paraphrase == "every") %>%
  mutate(Task = as.factor(Task),
         cModalPresent = as.numeric(ModalPresent) - mean(as.numeric(ModalPresent)),
         cTask = as.numeric(Task) - mean(as.numeric(Task)))

# Set contrasts
contrasts(every_data$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

```

- We found no significant interactions, except for a two-way interaction between Wh and Task only for who-questions.
- There were significant effects of Wh-Word on the every-paraphrase only for who- and how-, where every-ratings incresased for those Wh compared to When
```{r everyt-para model}
# m.every = lmer(normed_rating ~ cModalPresent*Wh*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id), data=every_data,REML=FALSE)
# saveRDS(m.every, "../models/model-contexts-every.rds")

every.model <- readRDS("../models/model-contexts-every.rds")
summary(every.model)
```

## The paraphrase

```{r subset to the-paraphrase, include=FALSE, warning=FALSE, echo=FALSE}
# Subset
the_data <- d %>%
  filter(paraphrase == "the") %>%
  mutate(Task = as.factor(Task),
         cModalPresent = as.numeric(ModalPresent) - mean(as.numeric(ModalPresent)),
         cTask = as.numeric(Task) - mean(as.numeric(Task)))

# Set contrasts
contrasts(the_data$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

```

- We found significant two-way interactions only between ModalPresent and WH-Word
```{r the-para model}
# m.the = lmer(normed_rating ~ cModalPresent*Wh*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id), data=the_data,REML=FALSE)
# saveRDS(m.the, "../models/model-contexts-the.rds")

the.model <- readRDS("../models/model-contexts-the.rds")
summary(the.model)

```


