---
title: "Exploratory analysis of context: Graphs"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(philentropy)
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")
```

```{r read in all the data, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
context_root = read.csv("../../../03_experiment/data/normed.csv") 
context_root$Task <- "context"
context_root$VerbLemma <- ""
context_root = context_root[,!(names(context_root) %in% c("X"))]

context_emb = read.csv("../../../04_experiment/data/normed.csv") 
context_emb$Task <- "context"
context_emb = context_emb[,!(names(context_emb) %in% c("X"))]


nocontext_root = read.csv("../../../05_experiment/data/normed_nocontext_root.csv")
nocontext_root$VerbLemma <- ""
nocontext_root$Task <- "nocontext"
nocontext_root = nocontext_root[,!(names(nocontext_root) %in% c("X"))]

nocontext_emb = read.csv("../../../06_experiment/data/normed_nocontext_embedded.csv")
nocontext_emb$Task <- "nocontext"
nocontext_emb = nocontext_emb[,!(names(nocontext_emb) %in% c("X"))]
```

```{r join all the dfs together, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
context <- full_join(context_root,context_emb)
nocontext <- full_join(nocontext_root,nocontext_emb)
d <- full_join(context, nocontext)

# sanity check the join
nrow(context_root) + nrow(context_emb) + nrow(nocontext_root) + nrow(nocontext_emb)
nrow(d)
```

# Plot the overall data with Task 

```{r aggregate for overall}
agr = d %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), 
            CILow = ci.low(normed_rating), 
            CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, 
         YMax = mean_rating + CIHigh) %>%
  drop_na()
dodge = position_dodge(.9)
```

```{r}
d %>% group_by(Task,paraphrase) %>% 
  summarize(mean_rating = mean(normed_rating), 
            sd = sd(normed_rating))
```


```{r plot overall}
ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=Task, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Task")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette) +
    scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/overall_Task.pdf",width=3,height=3)
```

```{r aggregate for Wh}
agr = d %>%
  group_by(Task,Wh,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), 
            CILow = ci.low(normed_rating), 
            CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, 
         YMax = mean_rating + CIHigh) %>%
  drop_na()
dodge = position_dodge(.9)
```


```{r plot overall}
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=Task, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  facet_wrap(~Wh,ncol=2) +
  xlab("paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Task")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette) +
    scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/overall_Task.pdf",width=3,height=3)
```

```{r aggregate for ModalPresent}
agr = d %>%
  group_by(Task,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), 
            CILow = ci.low(normed_rating), 
            CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, 
         YMax = mean_rating + CIHigh) %>%
  drop_na()
dodge = position_dodge(.9)
```


```{r plot modalpresent}
ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=Task, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  facet_wrap(~ModalPresent) +
  xlab("paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Task")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette) +
    scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/overall_Task.pdf",width=3,height=3)
```


# Denisity Plots

```{r aggregate by-item, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  group_by(Task, tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating))
```

## Mean Rating Denisity
```{r mean rating density, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in mean_rating
ggplot(data = agr, aes(x = mean_rating, fill=Task, color=Task)) +
  geom_density(alpha = .4) +
  facet_grid(~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/denisty_context_ratings.pdf",width=7,height=2)
```
## Standard Deviation Denisty
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in SD 
ggplot(data = agr, aes(x = sd, fill=Task, color=Task)) +
  geom_density(alpha = .4) +
  facet_grid(~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/denisty_context_sd.pdf",width=7,height=2)
```


# plot mean differences with linguistic factors too

## ModalPresent 
```{r aggregate for denisty with factors, warning=FALSE, echo=FALSE, message=FALSE}
# MODALPRESENT
agr = d %>%
  group_by(Task,ModalPresent,tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating))
```

### Mean Rating
```{r plot mean rating density with factors, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in mean_rating
ggplot(data = agr, aes(x = mean_rating, fill=Task, color=Task)) +
  geom_density(alpha = .4) +
  facet_grid(ModalPresent~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/denisty_context_MP_ratings.pdf",width=6,height=3)
```

### Standard Deviations
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in SD 
ggplot(data = agr, aes(x = sd, fill=Task, color=Task)) +
  geom_density(alpha = .4) +
  facet_grid(ModalPresent~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/denisty_context_MP_sd.pdf",width=6,height=3)
```

## Wh-Word
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# WH
agr = d %>%
  group_by(Task,Wh,tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating))
```

```{r}
# look at differences in mean_rating
ggplot(data = agr, aes(x = mean_rating, fill=Task, color=Task)) +
  geom_density(alpha = .4) +
  facet_grid(Wh~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
```


# Plot mean by-item differences, ordered by the size of the difference between Task

## Overall Relative difference between Context and NoContext Experiments
```{r, warning=FALSE, echo=FALSE, message=FALSE}
diffs = d %>%
  group_by(Task,paraphrase,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(difference = context-nocontext)

View(d[,d$tgrep_id=="100218:4"])
```


## Look at differnces due to factors
```{r aggregate over differences with factors}
diffs_agr <- diffs %>% 
  left_join(d,by=c("tgrep_id","paraphrase")) %>% 
  select(tgrep_id,difference,ModalPresent,Wh,paraphrase) %>% 
  unique()


View(diffs_agr)
```

```{r}
diffs_agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))

ggplot(diffs_agr,aes(x=paraphrase, y=mean_difference, alpha=ModalPresent, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Wh,ncol=2) +
  xlab("Paraphrase") +
  ylab("Mean Difference in rating Between Context and NoContext") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="ModalPresent")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette) +
    scale_alpha_discrete(range = c(.5,1))
```



## Mention-Some

### Absolute difference

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = abs(context-nocontext))
```


### Relative difference between Context and NoContext Experiments
```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext)
```



## Mention-All

### Absolute difference between Context and NoContext
```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "every") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = abs(context-nocontext))
```


### Relative difference between Context and NoContext Experiments
```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "every") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext)

```

