---
title: "Exploratory analysis of context: Examples"
author: Morgan Moyer
date: October 19, 2021
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(philentropy)
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")
```

```{r read in all the data, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
context_root = read.csv("../../../03_experiment/data/normed.csv") 
context_root$Task <- "context"
context_root$VerbLemma <- ""
context_root = context_root[,!(names(context_root) %in% c("X"))]

context_emb = read.csv("../../../04_experiment/data/normed.csv") 
context_emb$Task <- "context"
context_emb = context_emb[,!(names(context_emb) %in% c("X"))]


nocontext_root = read.csv("../../../05_experiment/data/normed_nocontext_root.csv")
nocontext_root$VerbLemma <- ""
nocontext_root$Task <- "nocontext"
nocontext_root = nocontext_root[,!(names(nocontext_root) %in% c("X"))]

nocontext_emb = read.csv("../../../06_experiment/data/normed_nocontext_embedded.csv")
nocontext_emb$Task <- "nocontext"
nocontext_emb = nocontext_emb[,!(names(nocontext_emb) %in% c("X"))]
```

```{r join all the dfs together, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
context <- full_join(context_root,context_emb)
nocontext <- full_join(nocontext_root,nocontext_emb)
d <- full_join(context, nocontext)

# sanity check the join
nrow(context_root) + nrow(context_emb) + nrow(nocontext_root) + nrow(nocontext_emb)
nrow(d)
```

```{r bring in corpus to see the context, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
corp = read.csv("../../../../corpus/analysis/swbd_contexts.csv")
names(corp)[names(corp) == "TGrepID"] <- "tgrep_id"
```


# Relative difference between Context and NoContext Experiments


## For A-paraphrase

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in descending order to see the high positive difference
  arrange(desc(difference)) 
```

### High Positive Difference

Examples for which the mean rating for 'a' was higher in the Context experiment than in the NoContext experiment. 

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```


```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

### High Negative Difference
Examples for which the mean rating for 'a' was higher in the NoContext experiment than in the Context experiment. 

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in ascending order to see the high negative difference
  arrange(difference) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```


```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

## For Every-paraphrase

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "every") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in descending order to see the high positive difference
  arrange(desc(difference)) 
```

### High Positive Difference

Examples for which the mean rating for 'a' was higher in the Context experiment than in the NoContext experiment. 

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```


```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

### High Negative Difference
Examples for which the mean rating for 'a' was higher in the NoContext experiment than in the Context experiment. 

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "every") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in ascending order to see the high negative difference
  arrange(difference) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```


```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

## For The-paraphrase

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "the") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in descending order to see the high positive difference
  arrange(desc(difference)) 
```

### High Positive Difference

Examples for which the mean rating for 'a' was higher in the Context experiment than in the NoContext experiment. 

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```


```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

### High Negative Difference
Examples for which the mean rating for 'a' was higher in the NoContext experiment than in the Context experiment. 

```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "the") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = context-nocontext) %>% 
  # arrange in ascending order to see the high negative difference
  arrange(difference) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```


```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

# Examples with the smallest difference between the two tasks


```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = abs(context-nocontext)) %>% 
  arrange(difference) 
```

1. The first smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


2. The second smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

5. The fifth smallest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```




# Look at absolute differences between Context and NoContext

Ignoring the directionality of the difference, let's see which examples 
change the most between the two tasks.

## First for A-Paraphrase
```{r, warning=FALSE, echo=FALSE, message=FALSE}
agr = d %>%
  filter(paraphrase == "a") %>%
  group_by(Task,tgrep_id) %>%
  summarize(mean_rating = mean(normed_rating)) %>%
  pivot_wider(names_from=Task,values_from=mean_rating) %>%
  group_by(tgrep_id) %>%
  summarize(difference = abs(context-nocontext)) %>% 
  arrange(desc(difference)) 
```

1. The first biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[1,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

2. The second biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[2,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


3. The third biggest.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[3,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```

4. The fourth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```

```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[4,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```


5. The fifth biggest.
```{r, warning=FALSE, echo=FALSE, message=FALSE}
corp %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(PreceedingContext) %>% 
  slice(1)
```


```{r , warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>% 
  select(Sentence) %>% 
  slice(1)
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
d %>%
  filter(tgrep_id == agr[5,]$tgrep_id) %>%
  group_by(Task,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating))
```