---
title: "Graphs for Experiment 1b, Embedded Questions Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")
```

# Read in data
```{r import data}
# Read database
corp = read.table("../../../corpus/results/swbd.tab",sep="\t",header=T,quote="")
# Read experimental data in
d = read.csv("../data/normed.csv")
nrow(d) # 174549

# rename item_id from corpus file
names(corp)[names(corp) == "Item_ID"] <- "tgrep_id"

# filter from the database the tgrep_ids from the raw data
corp_match = corp %>%
  filter(tgrep_id %in% d$tgrep_id)

# join dfs together
d <- left_join(d, corp_match, by="tgrep_id")

```

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating)) %>% 
  drop_na()

agr$YMin <- agr$mean_rating - ci.low(agr$mean_rating)
agr$YMax <- agr$mean_rating + ci.high(agr$mean_rating)
```

## Mean Rating
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in mean_rating
ggplot(data = agr, aes(x = mean_rating, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  # facet_grid(~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/ex1b_denisty_mean_ratings.pdf",width=6,height=3)
```

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1b_violin.pdf",width=6,height=4)
```


## Standard Deviation
```{r, warning=FALSE, echo=FALSE, message=FALSE}
# look at differences in SD 
ggplot(data = agr, aes(x = sd, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/ex1b_denisty_sd.pdf",width=6,height=3)
```

# Graph normed data 

## Overall
```{r}
agr = d %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()


dodge = position_dodge(.9)
ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  ylim(0,.6) +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/overall_noSQ.pdf",width=2,height=2)
```

## Graph Interaction between Modal and Wh
```{r}

agr = d %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

# Re-Order the WH-levels by overall composition of DB
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=ModalPresent, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Wh, ncol=2) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Modal present")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette) +
    scale_alpha_discrete(range = c(.5,1))

# ggsave("../graphs/modxwh_noSQ.pdf",width=3,height=4)
```

## Look at just Wh
```{r}
agr = d %>%
  group_by(paraphrase,Wh) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()
# Re-Order the WH-levels by overall composition of DB
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))
ggplot(agr,aes(x=Wh, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9))  +
  # ggtitle("Mean rating for Wh-Word") +
  xlab("Wh-Word") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/final_normed_wh.pdf")
```

## Look at just ModalPresent
```{r}
agr = d %>%
  group_by(paraphrase,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=ModalPresent, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  xlab("Modal Present") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# legend.spacing.y = unit(-10, 'cm'))
# guides(fill=guide_legend(title="Paraphrase"))
# ggsave("../graphs/final_normed_modalpresent.pdf")

```

## Graph MatrixVerb only
```{r}
verb_count = d %>%
  group_by(VerbLemma) %>%
  summarize(count = n())

View(verb_count)
nrow(verb_count) # 92 verbs

surp = subset(d,d$VerbLemma == "surprise")
nrow(surp)
agr = d %>%
  # Most frequent
  filter(VerbLemma %in% c("know","see","wonder","understand","be","understand","surprise","tell","figure","say","think","sure","learn","remember")) %>%
  group_by(paraphrase,VerbLemma,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()


ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=ModalPresent, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~VerbLemma) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Modal present")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette) +
    scale_alpha_discrete(range = c(.5,1))

# ggsave("../graphs/matrixverbs_threotical.pdf",width=10,height=10)
```

# Graph individual verbs
```{r }
agr = d %>%
  filter(VerbLemma == "know") %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

# Re-Order the WH-levels by overall composition of DB
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=ModalPresent, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Wh,ncol=2) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Modal present")) +
  ggtitle("Know") + 
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette) +
    scale_alpha_discrete(range = c(.5,1))

# ggsave("../graphs/modwh_know.pdf",width=3,height=4)
```

```{r Look at individual modals}
agr = d %>%   
  filter(ModalPresent %in% c("yes")) %>%
  group_by(Modal,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh)

ggplot(agr, aes(x=paraphrase,y=mean_rating,fill=paraphrase)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Modal,ncol=3) +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/modals.pdf",,width=4,height=5)
```


```{r Looking at individual items}
the_high = d %>%
  filter((paraphrase == "the")) %>% #  & (Wh == "why")
  group_by(tgrep_id,Sentence) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  filter(mean_rating > .5) %>%
  View()

a_high = d %>%
  filter((paraphrase == "a")) %>% #
  group_by(tgrep_id,Sentence, Question) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  # filter(mean_rating > .3) %>%
  View()

all_high = d %>%
  filter(paraphrase %in% c("every")) %>% 
  group_by(tgrep_id,Sentence) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  filter(mean_rating > .1) %>%
  View()


# Look at all ratings for a specific example
ex = test %>%
  filter(tgrep_id == "29177:41") %>%
  select(Sentence,Question,paraphrase,rating) %>%
  group_by(Sentence,Question,paraphrase) %>%
  summarize(mean_rating = mean(rating), sd = sd(rating)) %>%
  View()  

ex = d %>%
  filter(tgrep_id == "2512:34") %>%
  group_by(Sentence,Question,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
  View()


ex = test %>%
  filter(tgrep_id == "39551:19")
View(ex[,c("SentenceParse")])
```
(TOP (S (CC and) 
        (NP-SBJ-2 (PRP I)) 
        (VP (VBP have) 
            (VP (VBN been) 
                (VP (VBG debating) (SBAR (WHNP-1 (WP what)) (S (NP-SBJ (-NONE- *-2)) (VP (TO to) (VP (VB cook) (NP (-NONE- *T*-1)))))) (SBAR-PRP (IN because) (S (NP-SBJ (NP (CD one)) (PP (IN of) (NP (PRP$ my) (NNS guests)))) (VP (VBZ is) (NP-PRD (DT a) (NN vegetarian)))))))) (. .) (-DFL- E_S)))
